Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-07-13 prop_letter.tex
prop_letter.tex \section{Gleason} Update the proof...

\begin{example}\label{ex:three-dimensional-three-value}
  Given a three-dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,  let
  $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
  $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
  $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
 & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\,,
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\,,
\end{aligned}
\\
 &  & \unknown=\bar{\mu}_{3}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}_{3}$ is a QIVPM. Now
let $S_{1}=\left\{ \proj{0},\proj{\ps}\right\} $. Because
$\bar{\mu}_{3}(\proj{0})=\bar{\mu}_{3}(\proj{\ps})=\imposs$, we have
$\mu_{\rho}^{\mathrm{B}}(\proj{0})=\mu_{\rho}^{\mathrm{B}}(\proj{\ps})=0$
for any mixed
state\nb$\rho\in\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$.  Hence,
$\rho$ cannot be any state other than $\ket{2}$, the only pure state
orthogonal to both $\ket{0}$ and $\ket{\ps}$, and it is easy to verify
$\proj{2}$ is actually in
$\coreBorn\left(\bar{\mu}_{3},S_{1}\right)$. Similarly, let
$S_{2}=\left\{ \proj{0},\proj{\ps'}\right\} $. We have
$\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\left\{ \proj{1}\right\} $.
Therefore,
\begin{equation}
\coreBorn\left(\bar{\mu}_{3},\events\right)\subseteq\coreBorn\left(\bar{\mu}_{3},S_{1}\right)\cap\coreBorn\left(\bar{\mu}_{3},S_{2}\right)=\emptyset
\end{equation}
Thus, there is no state that is consistent with the QIVPM on all
projectors\nb$\events$, so Gleason's theorem does not hold for at least this
example.
\end{example}

@@

Foundational concepts in quantum mechanics, such as the Kochen-Specker and
Gleason theorems, rely in a very subtle way on the use of
unbounded resources. By assuming infinitely precise measurements,
these two insightful theorems underlie two fundamental aspects of
quantum mechanics. On the one hand, Kochen-Specker's result reveals a distinctive aspect of physical reality, the fact that it is contextual, and on the other hand, Gleason's theorem establishes a
relationship between quantum states and probabilities uniquely defined
by Born's rule.  Our goal
in this paper has been to analyze the physical consequences of a
mathematical framework that allows for finite precision measurements
by introducing the concept of quantum interval-valued probability. This
framework incorporates uncertainty in the measurement results by defining
fuzzy probability measures, and includes standard quantum measurement
as the particular instance of sharp, infinitely precise, intervals.
In addition, we showed how these two theorems emerge as limiting cases
of this same framework, thus connecting two seemingly unrelated
aspects of quantum physics. We noted that
{\it arbitrary\/} finite precision measurement conditions can nullify the main
tenets of both theorems. However, by carefully specifying experimental uncertainties, we were able to establish rigorous bounds on the validity of these two theorems. Therefore, we have established a context in which infinite precision quantum mechanical theories can be reconciled with finite precision quantum mechanical measurements, and have provided a possible resolution of the Meyer-Mermin debate on the impact of finite precision on the Kochen-Specker theorem \cite{PhysRevLett.83.3751,Mermin1999}.

>>>>

\begin{example}\label{ex:three-dimensional-three-value}
  Given a three-dimensional Hilbert space with an orthonormal basis
  $\left\{ \ket{0},\ket{1},\ket{2}\right\} $,  let
  $\mathscr{I}_{1}=\left\{ \necess,\imposs,\unknown\right\} $,
  $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
  $\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
\begin{subequations}
\begin{eqnarray}
 &  & \begin{aligned}\imposs & =\bar{\mu}_{3}(\mathbb{0})=\bar{\mu}_{3}(\proj{0})\\
 & =\bar{\mu}_{3}(\proj{\ps})=\bar{\mu}_{3}(\proj{\ps'})\,,
\end{aligned}
\\
 &  & \begin{aligned}\necess & =\bar{\mu}_{3}(\mathbb{1})=\bar{\mu}_{3}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}_{3}(\mathbb{1}-\proj{\ps})=\bar{\mu}_{3}(\mathbb{1}-\proj{\ps'})\,,
\end{aligned}
\\
 &  & \unknown=\bar{\mu}_{3}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
\end{subequations}
It is straightforward to verify that $\bar{\mu}_{3}$ is a QIVPM. Then we will
prove $\coreBorn\left(\bar{\mu}_{3},\events\right)$ is an empty set by
contradiction. Suppose there is a mixed
state\nb$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}\in\coreBorn\left(\bar{\mu}_{3},\events\right)$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. Since $\mu_{\rho}^{\mathrm{B}}(P)\in\bar{\mu}_{3}(P)$
for any\nb$P$, the mixed state\nb$\rho$ must satisfy
\begin{equation}
\melem{0}{\rho}{0}=\melem{\ps}{\rho}{\ps}=\melem{\ps'}{\rho}{\ps'}=0
\end{equation}
which implies $\ip{\phi_{j}}{0}=\ip{\phi_{j}}{\ps}=\ip{\phi_{j}}{\ps'}=0$
for all $j$. However, the last equation never holds. 
Thus, there is no state consistent with the QIVPM on all 
projectors\nb$P\in\events$, so Gleason's theorem does not hold for at least this
example.
\end{example}

@@

Foundational concepts in quantum mechanics, such as the Kochen-Specker and
Gleason theorems, rely in a very subtle way on the use of
unbounded resources. By assuming infinitely precise measurements,
these two insightful theorems underlie two fundamental aspects of
quantum mechanics. On the one hand, Kochen-Specker's result reveals a
distinctive aspect of physical reality, the fact that it is contextual, and, on the other hand, Gleason's theorem establishes a relationship between quantum states and probabilities uniquely defined
by Born's rule.  Our goal
in this paper has been to analyze the physical consequences of a
mathematical framework that allows for finite precision measurements
by introducing the concept of quantum interval-valued probability. This
framework incorporates uncertainty in the measurement results by defining
fuzzy probability measures, and includes standard quantum measurement
as the particular instance of sharp, infinitely precise, intervals.
In addition, we showed how these two theorems emerge as limiting cases
of this same framework, thus connecting two seemingly unrelated
aspects of quantum physics. We noted that
{\it arbitrary\/} finite precision measurement conditions can nullify the main
tenets of both theorems. However, by carefully specifying experimental uncertainties, we were able to establish rigorous bounds on the validity of these two theorems. Therefore, we have established a context in which infinite precision quantum mechanical theories can be reconciled with finite precision quantum mechanical measurements, and have provided a possible resolution of the Meyer-Mermin debate on the impact of finite precision on the Kochen-Specker theorem \cite{PhysRevLett.83.3751,Mermin1999}.
